1. Read the source code for each of the following three functions, puzzle out what they do, and then brainstorm better names.
```{r}
f1 <- function(string, prefix) {
  substr(string, 1, nchar(prefix)) == prefix
}
#f1 sees if a given string starts with the same characters as a given other string (prefix). It does this by taking in a string and a prefix and cutting the string to the same number of digits as the prefix (from its first character to that many characters) ------------ A BETTER NAME FOR f1 is: matching_start

f2 <- function(x) {
  if (length(x) <= 1) return(NULL)
  x[-length(x)]
}
#A BETTER NAME FOR f2 IS: remove_last   ------ this function takes in a vector If it is of length one it returns null otherwise it returns a vector of one shorter a length (namely missing the last value from the input)

f3 <- function(x, y) {
  rep(y, length.out = length(x))
}
#f3 takes in two vectors, x and y. It then gives you a vector the same length as x with the values in y. If x is longer than y it will recycle y's values to get this, if x is shorter it will truncate y. ------------ A BETTER NAME FOR f1 is: match_lengths

```


2. Compare and contrast rnorm() and MASS::mvrnorm(). How could you make them more consistent?
```{r}
?rnorm #rnorm takes in n, mean=0, sd=1 and so it returns to you n many digits selected from a random normal distribution (set by default to a mean of 0 and sd of 1)

?MASS::mvrnorm() #this takes in n, mu, sigma, tol=1e-6, empirical=F, EISPACK=F. This means it will return n many values from a multivariate normal distribution with mu and sigma properties (tol is by default set to 1e-6), empirical is only for the special case where mu and sigma are from empirical not population values and EISPACK is to prevent an error. It returns n many variables from the multivariable normal distribution you give it

#these differ because the multivariate normal distribution is a different distribution than the normal distribution (it is a higher dimensional generalization of it). The values will of course therefore differ. Setting mu=1 and sigma=1 can allow for somewhat similar values to setting mean=1 for the rnorm variable. By setting the means equal we can get more similar outputs
hist(MASS::mvrnorm(n=1000, mu=1,1))
hist(rnorm(1000, mean=1))
```
  
3. Use lapply() and an anonymous function to find the coefficient of variation (the standard deviation divided by the mean) for all columns in the mtcars dataset.
```{r}

```

4. Use vapply() to: a. Compute the standard deviation of every column in a numeric data frame. b. Compute the standard deviation of every numeric column in a mixed data frame. (Hint: you'll need to use vapply() twice.)
```{r}

```






