---
title: "Basic Webscraping"
---

<style type="text/css">
.table {

    width: 80%;
    margin-left:10%; 
    margin-right:10%;
}
</style>
```{r,setup, echo=FALSE, cache=TRUE}
## numbers >= 10^5 will be denoted in scientific notation,
## and rounded to 2 digits
options(scipen = 3, digits = 3)
```



## Exercises

1. Read the HTML content of the following URL with a variable called webpage: https://money.cnn.com/data/us_markets/ At this point, it will also be useful to open this web page in your browser.
```{r}
library(httr)
library(xml2)
library(rvest)#launching libraries for webscraping

savedurl <- "https://money.cnn.com/data/us_markets/"
read_html(savedurl)

```
2. Get the session details (status, type, size) of the above mentioned URL.
```{r}
geturl <- GET(savedurl) #GET gives all of the desired outputs, other functions can specifically find them
status_code(geturl) #finding status
content_type(savedurl) #finding type

```
3. Extract all of the sector names from the "Stock Sectors" table (bottom left of the web page.)
```{r}
table2 <- html_table(read_html(savedurl, "table"))[[2]] #make a dataframe from the table
table2 #look at the dataframe
table2[,1] #we want the first column of the df

```
4. Extract all of the "3 Month % Change" values from the "Stock Sectors" table.
```{r}
table2[,2] #now we want the second column from the df
```
5. Extract the table "What's Moving" (top middle of the web page) into a data-frame.
```{r}
table1 <- html_table(read_html(savedurl, "table"))[[1]] 
class(table1) #yayy its a dataframe
```
6. Re-construct all of the links from the first column of the "What's Moving" table.
Hint: the base URL is "https://money.cnn.com"
```{r}
#no clue how to start that! Nothing like this was in the videos!?
```

7. Extract the titles under the "Latest News" section (bottom middle of the web page.)
```{r}
html_nodes(readurl, css= "Latest News")
```
8. To understand the structure of the data in a web page, it is often useful to know what the underlying attributes are of the text you see. Extract the attributes (and their values) of the HTML element that holds the timestamp underneath the "What's Moving" table.
```{r}

```

9. Extract the values of the blue percentage-bars from the "Trending Tickers" table (bottom right of the web page.)
Hint: in this case, the values are stored under the "class" attribute.
```{r}

```

10. Get the links of all of the "svg" images on the web page.
```{r}

```



